Paper Figures and Text

### 2023-03-03 Fish Data Analysis/Paper_Figures.qmd
Adding Mixed Models

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)

@@

only_still_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
                 data = annushka_turning_data %>% filter(Flow == "Still Water"), 
                 family = binomial)

only_flow_model <- glm(turn_bool ~ Fish_Num_Ratio * Ablation * Darkness, 
                 data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), 
                 family = binomial)

@@

turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
Anova(turning_glm_still)

turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
Anova(turning_glm_flow)

@@

dark_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
                 data = all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark"), 
                 family = binomial)

dark_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark") %>%
                                                  mutate(predicted = predict(dark_eight_and_single_model, type="response")) %>%
                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                  summarise(predicted = predicted, n = n()) %>%
                                                  ungroup()

@@

ablation_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
                 data = all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated"), 
                 family = binomial)

ablation_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated")  %>%
                                                  mutate(predicted = predict(ablation_eight_and_single_model, type="response")) %>%
                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                  summarise(predicted = predicted, n = n()) %>%
                                                  ungroup()

@@

light_eight_and_single_model <- glm(turn_bool ~ Fish_Num_Ratio * Type, 
                 data = all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"), 
                 family = binomial)

light_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light")  %>%
                                                  mutate(predicted = predict(light_eight_and_single_model, type="response")) %>%
                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                  summarise(predicted = predicted, n = n()) %>%
                                                  ungroup()

@@

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph

still_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                               family = binomial)
Anova(still_light_turning_glm)

ablated_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                               family = binomial)
Anova(ablated_light_turning_glm)

dark_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                               family = binomial)
Anova(dark_light_turning_glm)

#Emmeans doesn't quite work since it makes it all into groups and not lines?
real_vs_sim_turning_glm <- glm(turn_bool ~ 0+Fish_Num_Ratio*Ablation*Darkness*Flow*Type, data = all_turning_data, family = binomial)
summary(real_vs_sim_turning_glm)
Anova(real_vs_sim_turning_glm)
emmeans(real_vs_sim_turning_glm, specs = pairwise ~ Type | Flow:Ablation:Darkness)

@@

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                           ungroup()
```

@@

nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
Anova(nnd_glm_still, test.statistic="F")
length((school_data %>% filter(Flow == "Still Water"))$NND)

nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
Anova(nnd_glm_flow, test.statistic="F")
length((school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))$NND)

@@

@@

## Startle Conditions

startle_school_data <- read.csv("Data/Startle_First_Half_Fish_School_Values.csv")
startle_school_data <- na.omit(startle_school_data)

startle_school_data <- startle_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
                           ungroup() %>% 
                           mutate(Exp_Label = paste0("Darkness Pre-Startle ",Trial))

startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
                                             mutate(Exp_Label = "Light") %>%
                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val,
                                                       School_Height, Height_Mean_Val, Height_SD_Val))

startle_school_data <- rbind(startle_school_data_light,startle_school_data) %>% 
                       mutate(Exp_Label = factor(Exp_Label)) %>%
                       mutate(Exp_Label = fct_relevel(Exp_Label,c("Light",
                                                                  "Darkness Pre-Startle 1",
                                                                  "Darkness Pre-Startle 5",
                                                                  "Darkness Pre-Startle 30")))

my_comparisons <- list(c("Light", "Darkness Pre-Startle 1"), c("Light", "Darkness Pre-Startle 5"), c("Light", "Darkness Pre-Startle 30"))

nnd_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 3, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

polar_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

speed_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

nnd_startle
polar_startle
speed_startle

ggsave("Paper Figures/startle_nnd.png", nnd_startle, width = 12, height = 7)

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)

@@

@@

@@

@@

@@

@@

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph
```

### Turning Stats Table Here

```{r}
turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
tgs_aov <- Anova(turning_glm_still)

turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
tgf_aov <- Anova(turning_glm_flow)

turning_results <- tibble(Flow_or_Still = c("Still","Still","Still","Still","Still","Flow","Flow","Flow","Flow","Flow"),
       Factor = c("Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness",
                  "Fish_Num_Ratio","Ablation","Darkness","Fish_Num_Ratio:Ablation","Fish_Num_Ratio:Darkness"),
       DF = c(rep(length(turning_glm_still$y)-3,5),rep(length(turning_glm_flow$y)-3,5)),
       LR_Chisq = c(tgs_aov$`LR Chisq`,tgf_aov$`LR Chisq`),
       P_Val = c(tgs_aov$`Pr(>Chisq)`,tgf_aov$`Pr(>Chisq)`),
       Is_Sig = P_Val < 0.05)

# Single vs Eight fish
light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                               family = binomial)
ltg_aov <- Anova(light_turning_glm)

ablated_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                               family = binomial)
altg_aov <- Anova(ablated_turning_glm)

dark_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                               family = binomial)
dtg_aov <- Anova(dark_turning_glm)

single_vs_eight_results <- tibble(Condition = c("Light","Light","Ablated","Ablated","Darkness","Darkness"),
       Factor = c("Type","FNR:Type","Type","FNR:Type","Type","FNR:Type"),
       DF = c(rep(length(light_turning_glm$y)-3,2),rep(length(ablated_turning_glm$y)-3,2),rep(length(dark_turning_glm$y)-3,2)),
       LR_Chisq = c(ltg_aov$`LR Chisq`[2:3],altg_aov$`LR Chisq`[2:3],dtg_aov$`LR Chisq`[2:3]),
       P_Val = c(ltg_aov$`Pr(>Chisq)`[2:3],altg_aov$`Pr(>Chisq)`[2:3],dtg_aov$`Pr(>Chisq)`[2:3]),
       Is_Sig = P_Val < 0.05)

turning_results
single_vs_eight_results

@@

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%

                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Date = paste(Year,Month,Day,sep="_"),
                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
                           group_by(Date_Trial) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup() %>%
                           # ###

                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                           ungroup()
```

@@

@@

### School Stats Table Here

nnd_glmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
nnd_s_aov_me <- Anova(nnd_glmer_still)

nnd_glmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
nnd_f_aov_me <- Anova(nnd_glmer_flow)

height_glmer_still <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
height_s_aov_me <- Anova(height_glmer_still)

height_glmer_flow <- lmer(School_Height ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
height_f_aov_me <- Anova(height_glmer_flow)

polar_glmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
polar_s_aov_me <- Anova(polar_glmer_still)

polar_glmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
polar_f_aov_me <- Anova(polar_glmer_flow)

speed_glmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
speed_s_aov_me <- Anova(speed_glmer_still)

speed_glmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
speed_f_aov_me <- Anova(speed_glmer_flow)

area_glmer_still <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
area_s_aov_me <- Anova(area_glmer_still)

area_glmer_flow <- lmer(Area ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
area_f_aov_me <- Anova(area_glmer_flow)

groups_glmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
groups_s_aov_me <- Anova(groups_glmer_still)

groups_glmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
groups_f_aov_me <- Anova(groups_glmer_flow)

glmm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
       Condition = rep(c("Ablation","Darkness"), 12),
       DF = rep(c(length(nnd_glmer_still@resp$y)-3,length(nnd_glmer_flow@resp$y)-3),12),
       Chisq = c(nnd_s_aov_me$Chisq[1:2],nnd_f_aov_me$Chisq[1:2],
                 height_s_aov_me$Chisq[1:2],height_f_aov_me$Chisq[1:2],
                 polar_s_aov_me$Chisq[1:2],polar_f_aov_me$Chisq[1:2],
                 speed_s_aov_me$Chisq[1:2],speed_f_aov_me$Chisq[1:2],
                 area_s_aov_me$Chisq[1:2],area_f_aov_me$Chisq[1:2],
                 groups_s_aov_me$Chisq[1:2],groups_f_aov_me$Chisq[1:2]),

       P_Val = c(nnd_s_aov_me$`Pr(>Chisq)`[1:2],nnd_f_aov_me$`Pr(>Chisq)`[1:2],
                 height_s_aov_me$`Pr(>Chisq)`[1:2],height_f_aov_me$`Pr(>Chisq)`[1:2],
                 polar_s_aov_me$`Pr(>Chisq)`[1:2],polar_f_aov_me$`Pr(>Chisq)`[1:2],
                 speed_s_aov_me$`Pr(>Chisq)`[1:2],speed_f_aov_me$`Pr(>Chisq)`[1:2],
                 area_s_aov_me$`Pr(>Chisq)`[1:2],area_f_aov_me$`Pr(>Chisq)`[1:2],
                 groups_s_aov_me$`Pr(>Chisq)`[1:2],groups_f_aov_me$`Pr(>Chisq)`[1:2]),

       Is_Sig = P_Val < 0.05)

glmm_school_stats_table

nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
nnd_s_aov <- Anova(nnd_glm_still)

nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
nnd_f_aov <- Anova(nnd_glm_flow)

height_glm_still <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
height_s_aov <- Anova(height_glm_still)

height_glm_flow <- glm(School_Height ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
height_f_aov <- Anova(height_glm_flow)

polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
polar_s_aov <- Anova(polar_glm_still)

polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
polar_f_aov <- Anova(polar_glm_flow)

speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
speed_s_aov <- Anova(speed_glm_still)

speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
speed_f_aov <- Anova(speed_glm_flow)

area_glm_still <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
area_s_aov <- Anova(area_glm_still)

area_glm_flow <- glm(Area ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
area_f_aov <- Anova(area_glm_flow)

groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
groups_s_aov <- Anova(groups_glm_still)

groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
groups_f_aov <- Anova(groups_glm_flow)

glm_school_stats_table <- tibble(Stat = c(rep("NND",4),rep("Height",4),rep("Polarization",4),rep("Speed",4),rep("Area",4),rep("Groups",4)),
       Flow_or_Still = rep( c(rep("Still",2) , rep("Flow",2)), 6),
       Condition = rep(c("Ablation","Darkness"), 12),
       DF = rep(c(length(nnd_glm_still$y)-3,length(nnd_glm_flow$y)-3),12),
       Chisq = c(nnd_s_aov$`LR Chisq`[1:2],nnd_f_aov$`LR Chisq`[1:2],
                 height_s_aov$`LR Chisq`[1:2],height_f_aov$`LR Chisq`[1:2],
                 polar_s_aov$`LR Chisq`[1:2],polar_f_aov$`LR Chisq`[1:2],
                 speed_s_aov$`LR Chisq`[1:2],speed_f_aov$`LR Chisq`[1:2],
                 area_s_aov$`LR Chisq`[1:2],area_f_aov$`LR Chisq`[1:2],
                 groups_s_aov$`LR Chisq`[1:2],groups_f_aov$`LR Chisq`[1:2]),

       P_Val = c(nnd_s_aov$`Pr(>Chisq)`[1:2],nnd_f_aov$`Pr(>Chisq)`[1:2],
                 height_s_aov$`Pr(>Chisq)`[1:2],height_f_aov$`Pr(>Chisq)`[1:2],
                 polar_s_aov$`Pr(>Chisq)`[1:2],polar_f_aov$`Pr(>Chisq)`[1:2],
                 speed_s_aov$`Pr(>Chisq)`[1:2],speed_f_aov$`Pr(>Chisq)`[1:2],
                 area_s_aov$`Pr(>Chisq)`[1:2],area_f_aov$`Pr(>Chisq)`[1:2],
                 groups_s_aov$`Pr(>Chisq)`[1:2],groups_f_aov$`Pr(>Chisq)`[1:2]),

       Is_Sig = P_Val < 0.05)

glm_school_stats_table

sum(glm_school_stats_table$Is_Sig == glmm_school_stats_table$Is_Sig)
sum(glm_school_stats_table$Is_Sig == 1 & glmm_school_stats_table$Is_Sig == 1) / sum(glm_school_stats_table$Is_Sig == 1)

@@
